Simple connectome inference from partial\\[1ex] correlation statistics in calcium imaging

### 2014-09-12 oral/slides.tex
new version slides

\usepackage{textpos}

@@

@@

@@

\title{Simple connectome inference from partial\\[1ex]
correlation statistics in calcium imaging}
\author{{\small Antonio Sutera, Arnaud Joly, Vincent François-Lavet, Zixiao Aaron Qiu\\[1ex] Gilles Louppe, Damien Ersnt and Pierre Geurts.}}
\date{}

@@

\begin{textblo}
\begin{minipage}{0.95\linewidth}
{\color{red} \textbf{masking} effects}
\end{minipage}

\begin{minipage}{0.95\linewidth}
{\color{red} \textbf{masking} effects}
\end{minipage}

% \begin{tabular*}{\textwidth}{l r} \hline
% &\multirow{3}{*}{\includegraphics[width=2cm]{images/miss.png} \includegraphics[width=2cm]{images/hidden.png}}\\

% {\color{red} \textbf{masking} effects}
% & \\ 
% & \\

% \item {\color{red} \textbf{masking} effects},
% \includegraphics[width=2cm]{images/miss.png} \includegraphics[width=2cm]{images/hidden.png}
% \item {\color{red} \textbf{low} sampling rate},
% \includegraphics[width=4cm]{images/slowsamplingrate.png}
% \item {\color{red} \textbf{slow} decay} of fluorescence.
% \includegraphics[width=4cm]{images/original_curve_gr}
% \end{itemize}

@@

{\color{red} How-to}:
\begin{enumerate}
\item \textbf{Deal} with calcium fluorescence signals: {\color{i6blue} signal processing}.
\item \textbf{Find} the network: the {\color{i6blue} {inference} method}.
\item \textbf{Improve} the method: our {\color{i6blue} {tricks}}.
\end{enumerate}\vskip5pt

@@

\begin{overprint}
\onslide<1> 
a-b

\onslide<2>
a-b-c

\onslide<3>
a-b-c-d

\onslide<4>
a-b-c-d-e
\end{overprint}

@@

\begin{columns}
\begin{column}{0.5\linewidth}
diag
\end{column}
\begin{column}{0.5\linewidth}

\begin{itemize}
\item[{\color{green} \cmark}] Only direct associations
\item[{\color{green} \cmark}] Filter out spurious indirect effects
\item[{\color{green} \cmark}] Symmetric \\[5ex]
\item[{\color{red} \xmark}] Edge orientation
\item[{\color{red} \xmark}] Sensitive to the value of parameters in the filtering process
\end{itemize}

@@

\begin{frame}
\frametitle{Each stage of our solution is good!}

\begin{table}[t]
\caption{Performance on \textit{normal-1,2,3,4} with partial correlation and different filtering functions.}
\label{tab:comparison}
\centering
\tiny
\begin{tabular}{| l | c c c c | c c c c |}
\hline
& \multicolumn{4}{c|}{AUROC} & \multicolumn{4}{c|}{AUPRC} \\
\textit{Method} $\backslash$ \textit{normal-} & \textit{1} & \textit{2} & \textit{3} & \textit{4} & \textit{1} & \textit{2} & \textit{3} & \textit{4} \\
\hline
\hline
No  filtering       					& 0.777 & 0.767 & 0.772 & 0.774 & 0.070 & 0.064 & 0.068 & 0.072\\
$ h \circ g \circ f_1$                  & 0.923 & 0.925 & 0.923 & 0.922 & 0.311 & 0.315 & 0.313 & 0.304\\
$ w \circ h \circ g \circ f_1$          & 0.931 & 0.929 & 0.928 & 0.926 & 0.326 & 0.323 & 0.319 & 0.303\\
+ PCA         							& 0.932 & 0.930 & 0.928 & 0.926 & 0.355 & 0.353 & 0.350 & 0.333\\
Averaging           					& 0.937 & 0.935 & 0.935 & 0.931 & 0.391 &  0.390 &  0.385 & 0.375\\
Full method           					& \textbf{0.943} & \textbf{0.942} & \textbf{0.942} & \textbf{0.939} & \textbf{0.403} & \textbf{0.404} & \textbf{0.398} & \textbf{0.388}\\
\hline
\end{tabular}
\end{table}

@@

\begin{table}[t]

\caption{Performance on \textit{normal-1,2,3,4} with different methods.}
\label{tab:comparison}
\centering
\tiny
\begin{tabular}{| l | c c c c | c c c c |}
\hline
& \multicolumn{4}{c|}{AUROC} & \multicolumn{4}{c|}{AUPRC} \\
\textit{Method} $\backslash$ \textit{normal-} & \textit{1} & \textit{2} & \textit{3} & \textit{4} & \textit{1} & \textit{2} & \textit{3} & \textit{4} \\
\hline
\hline
Averaging           					& 0.937 & 0.935 & 0.935 & 0.931 & 0.391 &  0.390 &  0.385 & 0.375\\
Full method           					& \textbf{0.943} & \textbf{0.942} & \textbf{0.942} & \textbf{0.939} & \textbf{0.403} & \textbf{0.404} & \textbf{0.398} & \textbf{0.388}\\
\hline
PC & 0.886 & 0.884 & 0.891 &  0.877 & 0.153 & 0.145 & 0.170 & 0.132\\
GTE & 0.890 & 0.893 & 0.894 & 0.873 & 0.171 & 0.174 & 0.197 & 0.142\\
GENIE3 & 0.892 & 0.891 & 0.887 & 0.887 & 0.232 & 0.221 & 0.237 & 0.215 \\
\hline
\end{tabular}
\end{table}

>>>>

\usepackage[absolute,overlay]{textpos}

@@

\usepackage[pdf]{pstricks}

@@

\setlength{\TPHorizModule}{\paperwidth}
\setlength{\TPVertModule}{\paperheight}

@@

\title{Simple connectome inference from partial\\[1ex]
correlation statistics in calcium imaging}
\author{{\small Antonio Sutera, Arnaud Joly, Vincent François-Lavet, Zixiao Aaron Qiu\\[1ex] Gilles Louppe, Damien Ernst and Pierre Geurts.}}
\date{}

\addtobeamertemplate{navigation symbols}{}{%
    \usebeamerfont{footline}%
    \usebeamercolor[fg]{footline}%
    \hspace{1em}%
    \insertframenumber/\inserttotalframenumber
}

@@

\begin{textblock}{0.3}(0.01,0.35)
\begin{itemize}
\item{\color{red}\textbf{masking} effects}
\end{itemize}
\end{textblock}

\begin{textblock}{0.5}(0.55,0.25)

% \begin{pspicture}(20,20)

% 	\pscircle[linewidth=2pt](10,10)

%     \end{pspicture}
% \scalebox{1}{\includegraphics[width=\paperwidth]{slides-pics.pdf}}

\includegraphics[width=2cm]{images/miss.png} \includegraphics[width=2cm]{images/hidden.png}

% \begin{pspicture}(0.99\textwidth,0.99\textheight)

% \psframe[linewidth=0pt, linecolor=black!1](0,0)(\paperwidth,)

%  	       	% \psline[linewidth=2pt,linecolor=lightblue, linestyle=dashed]{->}(0.5\paperwidth,\paperheight)(0.5\paperwidth,0)

%     \end{pspicture}
% \scalebox{1}{\includegraphics[width=\paperwidth]{slides-pics.pdf}}

\end{textblock}

\begin{textblock}{1}(0.01,0.55)
\begin{itemize}
\item {\color{red} \textbf{low} sampling rate}
\end{itemize}
\end{textblock}

\begin{textblock}{1}(0.40,0.45)
\includegraphics[width=3.5cm]{images/original_curve_sampling.pdf} $\Rightarrow$
\includegraphics[width=3.5cm]{images/original_curve_sampling_2.pdf}
\end{textblock}

\begin{textblock}{1}(0.01,0.75)
\begin{itemize}
\item {\color{red} \textbf{slow} decay} of fluorescence.
\end{itemize}
\end{textblock}

\begin{textblock}{1}(0.55,0.75)
\includegraphics[width=3.5cm]{images/original_curve_gr_2.pdf}
\end{textblock}

% \begin{textblo}
% \begin{minipage}{0.95\linewidth}
% {\color{red} \textbf{masking} effects}
% \end{minipage}

% \begin{minipage}{0.95\linewidth}
% {\color{red} \textbf{masking} effects}
% \end{minipage}

% % \begin{tabular*}{\textwidth}{l r} \hline
% % &\multirow{3}{*}{\includegraphics[width=2cm]{images/miss.png} \includegraphics[width=2cm]{images/hidden.png}}\\

% % {\color{red} \textbf{masking} effects}
% % & \\ 
% % & \\

% % \item {\color{red} \textbf{masking} effects},
% % \includegraphics[width=2cm]{images/miss.png} \includegraphics[width=2cm]{images/hidden.png}
% % \item {\color{red} \textbf{low} sampling rate},
% % \includegraphics[width=4cm]{images/slowsamplingrate.png}
% % \item {\color{red} \textbf{slow} decay} of fluorescence.
% % \includegraphics[width=4cm]{images/original_curve_gr}
% % \end{itemize}

@@

{\color{red} How-to}:
\begin{enumerate}
\item \textbf{Deal} with calcium fluorescence signals: {\color{i6blue} signal processing}.
\item \textbf{Find} the network: the {\color{i6blue} {inference} method}.
\item \textbf{Improve} the method: {\color{i6blue} {averaging}} and {\color{i6blue} {tuning}}.
\end{enumerate}\vskip5pt

@@

\begin{textblock}{1}(0.00,0.001)
\begin{pspicture}(0.99\textwidth,0.99\textheight)

\psframe[linewidth=0pt, linecolor=black!1](0,0)(\paperwidth,\paperheight)

 	       	% \psline[linewidth=2pt,linecolor=lightblue, linestyle=dashed]{->}(0.5\paperwidth,\paperheight)(0.5\paperwidth,0)

\psline[linewidth=2pt, linecolor=lightblue, linestyle=dashed]{->}(0.15\paperwidth,0.75\paperheight)(0.15\paperwidth,0.5\paperheight)

\psline[linewidth=2pt, linecolor=lightblue, linestyle=dashed]{->}(0.85\paperwidth,0.5\paperheight)(0.85\paperwidth,0.60\paperheight)

\psarc[linewidth=2pt,linecolor=lightblue, linestyle=dashed]{->}(0.33\paperwidth,0.40\paperheight){2.5}{180}{275}

\psarc[linewidth=2pt,linecolor=lightblue, linestyle=dashed]{->}(0.65\paperwidth,0.40\paperheight){2.5}{270}{325}

\psline[linewidth=4pt, linecolor=lightblue, linestyle=solid]{->}(0.30\paperwidth,0.75\paperheight)(0.7\paperwidth,0.75\paperheight)

\rput(0.12\paperwidth,0.58\paperheight){{\color{lightblue} 1}}
\rput(0.20\paperwidth,0.16\paperheight){{\color{lightblue} 2}}
\rput(0.77\paperwidth,0.16\paperheight){{\color{lightblue} 3}}
\rput(0.88\paperwidth,0.555\paperheight){{\color{lightblue} 4}}
\rput(0.50\paperwidth,0.80\paperheight){{\color{lightblue} \textbf{Signal processing}}}

    \end{pspicture}
\scalebox{1}{\includegraphics[width=\paperwidth]{images/signal_processing.pdf}}
\end{textblock}

\begin{textblock}{1}(0.01,0.15)
\includegraphics[width=3.5cm]{images/original_curve_2.pdf}
\end{textblock}

\begin{textblock}{1}(0.01,0.50)
\includegraphics[width=3.5cm]{images/filter_curve_2.pdf}
\end{textblock}

\begin{textblock}{1}(0.35,0.75)
\includegraphics[width=3.5cm]{images/diff_curve_2.pdf}
\end{textblock}

\begin{textblock}{1}(0.70,0.50)
\includegraphics[width=3.5cm]{images/threshold_curve_3.pdf}
\end{textblock}

\begin{textblock}{1}(0.70,0.15)
\includegraphics[width=3.5cm]{images/weights_curve_3.pdf}
\end{textblock}

\begin{textblock}{0.35}(0.3,0.3)

{\footnotesize 
\begin{enumerate}
\item Applying a low-pass filter
\item Applying a high-pass filer
\item Applying a hard-threshold filter 
\item Magnify the importance of spikes that occur in case of low global activity
\end{enumerate}}

\end{textblock}

% \onslide<2>
% a-b-c

% \onslide<3>
% a-b-c-d

% \onslide<4>
% a-b-c-d-e
% \end{overprint}

@@

\begin{columns}
\begin{column}{0.55\linewidth}

\includegraphics[width=6cm]{images/network.pdf}
\vspace{10pt}
\textbf{\textit{Partial correlation}} coefficient $p_{i,j}$ between neurons $i$ and $j$ defined by:
\begin{align*}
p_{i,j} =
-\frac{\Sigma^{-1}_{ij}}{\sqrt{\Sigma^{-1}_{ii} \Sigma^{-1}_{jj}}}, \label{eq:inverse}
\end{align*}

\begin{column}{0.45\linewidth}

\textbf{Advantages and drawbacks}:
\begin{itemize}
\item[{\color{green} \cmark}] Only direct associations
\item[{\color{green} \cmark}] Filter out spurious indirect effects
\item[{\color{green} \cmark}] Symmetric 
\item[{\color{green} \cmark}] Easy to compute \\ (with lots of data) \\[2ex]
\item[{\color{red} \xmark}] Edge orientation
\item[{\color{red} \xmark}] Sensitive to the value of parameters in the filtering process
\end{itemize}

@@

\begin{frame}
\frametitle{Each stage of our solution brings some improvement}

\begin{center}
\textit{Average scores on normal-{1,2,3,4} datasets.
}
\includegraphics[width=8cm]{images/data_stage.png}
\end{center}

% \begin{table}[t]
% \caption{Performance on \textit{normal-1,2,3,4} with partial correlation and different filtering functions.}
% \label{tab:comparison}
% \centering
% \tiny
% \begin{tabular}{| l | c c c c | c c c c |}
% \hline
% & \multicolumn{4}{c|}{AUROC} & \multicolumn{4}{c|}{AUPRC} \\
% \textit{Method} $\backslash$ \textit{normal-} & \textit{1} & \textit{2} & \textit{3} & \textit{4} & \textit{1} & \textit{2} & \textit{3} & \textit{4} \\
% \hline
% \hline
% No  filtering       					& 0.777 & 0.767 & 0.772 & 0.774 & 0.070 & 0.064 & 0.068 & 0.072\\
% $ h \circ g \circ f_1$                  & 0.923 & 0.925 & 0.923 & 0.922 & 0.311 & 0.315 & 0.313 & 0.304\\
% $ w \circ h \circ g \circ f_1$          & 0.931 & 0.929 & 0.928 & 0.926 & 0.326 & 0.323 & 0.319 & 0.303\\
% + PCA         							& 0.932 & 0.930 & 0.928 & 0.926 & 0.355 & 0.353 & 0.350 & 0.333\\
% Averaging           					& 0.937 & 0.935 & 0.935 & 0.931 & 0.391 &  0.390 &  0.385 & 0.375\\
% Full method           					& \textbf{0.943} & \textbf{0.942} & \textbf{0.942} & \textbf{0.939} & \textbf{0.403} & \textbf{0.404} & \textbf{0.398} & \textbf{0.388}\\
% \hline
% \end{tabular}
% \end{table}

@@

\begin{center}
\textit{Average scores on normal-{1,2,3,4} datasets.
}
\includegraphics[width=9cm]{images/data_method.png}
\end{center}
% \begin{table}[t]

% \caption{Performance on \textit{normal-1,2,3,4} with different methods.}
% \label{tab:comparison}
% \centering
% \tiny
% \begin{tabular}{| l | c c c c | c c c c |}
% \hline
% & \multicolumn{4}{c|}{AUROC} & \multicolumn{4}{c|}{AUPRC} \\
% \textit{Method} $\backslash$ \textit{normal-} & \textit{1} & \textit{2} & \textit{3} & \textit{4} & \textit{1} & \textit{2} & \textit{3} & \textit{4} \\
% \hline
% \hline
% Averaging           					& 0.937 & 0.935 & 0.935 & 0.931 & 0.391 &  0.390 &  0.385 & 0.375\\
% Full method           					& \textbf{0.943} & \textbf{0.942} & \textbf{0.942} & \textbf{0.939} & \textbf{0.403} & \textbf{0.404} & \textbf{0.398} & \textbf{0.388}\\
% \hline
% PC & 0.886 & 0.884 & 0.891 &  0.877 & 0.153 & 0.145 & 0.170 & 0.132\\
% GTE & 0.890 & 0.893 & 0.894 & 0.873 & 0.171 & 0.174 & 0.197 & 0.142\\
% GENIE3 & 0.892 & 0.891 & 0.887 & 0.887 & 0.232 & 0.221 & 0.237 & 0.215 \\
% \hline
% \end{tabular}
% \end{table}
